\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
comma in list of adjectives
fix space before comma

This paper is structured as follows, first a brief radiation transport-focused introduction to computer descriptions of geometry, followed by an explanation of the design 
and implementation of \PYGEOMETRY{}. The sections that follow describe how \PYGEOMETRY{} can be used to perform rapid geometric modelling, conversion from 
FLUKA to GDML, GDML to FLUKA and CAD to GDML. The paper concludes with an example of a composite complex system consisting of components drawn from 
all the supported  geometry input files formats.

\section{Computer descriptions of geometry} \label{sec:geometric}
Central to a computer-readable geometry is how a solid is defined in three dimensions. There are numerous different ways to describe a
geometry, including constructive solid geometry (CSG) , boundary representation (BREP) and tessellated polygons, which are described 
briefly in the following sections.  The Geant4 geometry specification is a mixture of geometry modelling techniques and described in detail last.

>>>>

This paper is structured as follows, first a brief radiation transport-focused introduction to computer descriptions of geometry, followed by an explanation of the design 
and implementation of \PYGEOMETRY{}. The sections that follow describe how \PYGEOMETRY{} can be used to perform rapid geometric modelling, conversion from 
FLUKA to GDML, GDML to FLUKA and CAD to GDML. The paper concludes with an example of a composite, complex system consisting of components drawn from 
all the supported  geometry input files formats.

\section{Computer descriptions of geometry} \label{sec:geometric}
Central to a computer-readable geometry is how a solid is defined in three dimensions. There are numerous different ways to describe a
geometry, including constructive solid geometry (CSG), boundary representation (BREP) and tessellated polygons, which are described 
briefly in the following sections.  The Geant4 geometry specification is a mixture of geometry modelling techniques and described in detail last.
